Analysis Stand Features 

### 2017-05-15 analysis/analysis_stand_features.Rmd
update pdf

---
title: "Analysis Stand Features "
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 May"
output:  
  md_document:
    toc: true
    variant: markdown_github
---

>>>>

---
title: "Analysis Stand Features "
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 May"
output: pdf_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```
